
## 📅 Event Overview

-   **Dates:** 3rd–4th September 2025

-   **Time:** 10:00 – 17:00 (both days)

-   **Format:** Hybrid

    -   **Virtual:** Microsoft Teams. Links are provided in the agenda for meetings that include everyone involved in the hackathon. The agenda also includes links to drop-in sessions for specific topics. For meetings that are team specific, teams will set up their own meetings.

    -   **In-Person:** Coventry, Darlington, London and Sheffield.

-   By taking part in this hackathon, you agree to follow our [Code of conduct](https://educationgovuk.sharepoint.com/:u:/r/sites/lveesfa00074/SSU%20%20Open%20sharing/Away%20days/2025%20statistics%20away%20day/Hackathon_2025/code_of_conduct.html?csf=1&web=1&e=fVwrwx).

------------------------------------------------------------------------

## 📝 Rooms and Agenda {#agenda}

::: panel-tabset
### 📅 Day 1: 3rd September 2025

**Rooms booked**

```{r, echo=FALSE, warning=FALSE}

rooms <- data.frame(
  Location = c("Coventry", "Darlington", "London", "Sheffield"),
  Room = c("CH S2.4 (10) VC", "BGH L2-3 (10) VC", "SB LG.01/LG.02 (20) VC", "SPP 4-10 (10) VC")
)
knitr::kable(rooms, format = "markdown")

```
**Agenda**
```{r, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)

schedule_1 <- data.frame(
  Time = c(
    "10:00 – 10:30", 
    "10:30 – 11:00",  
    "11:00 – 12:00", 
    "12:00 – 13:00",
    "13:00 – 13:30", 
    "13:30 – 14:30", 
    "14:30 – 15:00",
    "15:00 – 16:30",
    "16:30 – 17:00"
  ),
  Activity = c(
    "🟢 [Welcome & Kickoff on MS Teams](https://teams.microsoft.com/l/meetup-join/19%3ameeting_OTRkOTg3NzQtNzQ1OS00OWQ2LWJhMjItMmNlZDE5YzNjNmJh%40thread.v2/0?context=%7b%22Tid%22%3a%22fad277c9-c60a-4da1-b5f3-b3b8b34a82f9%22%2c%22Oid%22%3a%2273293cd8-b712-4b8b-a99d-b7788ea2a6bd%22%7d)",
    "🧠 Project Planning", 
    "💻 Hacking Session #1", 
    "🍽️ Lunch Break",
    "💬 Team Check-In 💻",
    "💻 Hacking Session #2", 
    "☕ Afternoon Break",
    "💻 Hacking Session #3",
    "💬 Team Check-In & Wrap-Up"
  ),
  Details = c(
    "- Overview of hackathon goals & schedule <br>- Team introductions",
    
    
    "- Teams set up their own meetings to brainstorm and finalise project ideas <br>- Mentors available for guidance",

    
    "- [MS Teams Drop-in: Git (11:30–12:00)](https://teams.microsoft.com/l/meetup-join/19%3ameeting_NmM5YmZiOGMtMGQxYi00ZTQzLWI2ZjUtYjNhMjlhNDE0MTJm%40thread.v2/0?context=%7b%22Tid%22%3a%22fad277c9-c60a-4da1-b5f3-b3b8b34a82f9%22%2c%22Oid%22%3a%2273293cd8-b712-4b8b-a99d-b7788ea2a6bd%22%7d) <br>- Begin development",

    
    "- Lunch is not provided but feel free to bring your own",
    
    "- Teams set up their own meetings for internal team sync <br>- Progress updates",

    
    "- [MS Teams Drop-in: RShiny (13:30–14:00)](https://teams.microsoft.com/l/meetup-join/19%3ameeting_MTU2ZTlkNzktMjhhNC00NGQwLWEwMzgtZjAwM2NjYmE3ZTE1%40thread.v2/0?context=%7b%22Tid%22%3a%22fad277c9-c60a-4da1-b5f3-b3b8b34a82f9%22%2c%22Oid%22%3a%2273293cd8-b712-4b8b-a99d-b7788ea2a6bd%22%7d) <br>- [MS Teams Drop-in: EES API (14:00–14:30)](https://teams.microsoft.com/l/meetup-join/19%3ameeting_NmI5NzJjMTctOWY4MS00MzQ4LTgyODEtNzJjNmEwZjNlMmI5%40thread.v2/0?context=%7b%22Tid%22%3a%22fad277c9-c60a-4da1-b5f3-b3b8b34a82f9%22%2c%22Oid%22%3a%2273293cd8-b712-4b8b-a99d-b7788ea2a6bd%22%7d) <br>- Continue development",
    
    "- Take a break from the screen!",
    
      "- [MS Teams Drop-in: LLMs (15:00–15:30)](https://teams.microsoft.com/l/meetup-join/19%3ameeting_NmIzNTM3YjQtYTJiMi00NjcyLWIzMTQtMWY0YzNiMDJiYmU5%40thread.v2/0?context=%7b%22Tid%22%3a%22fad277c9-c60a-4da1-b5f3-b3b8b34a82f9%22%2c%22Oid%22%3a%2273293cd8-b712-4b8b-a99d-b7788ea2a6bd%22%7d) <br>- [MS Teams Drop-in: Automated QA (15:30–16:00)](https://teams.microsoft.com/l/meetup-join/19%3ameeting_ZTI5N2UyNGMtOTUwYi00ODllLWJmZGItM2FkOTExM2RhZmQ4%40thread.v2/0?context=%7b%22Tid%22%3a%22fad277c9-c60a-4da1-b5f3-b3b8b34a82f9%22%2c%22Oid%22%3a%2273293cd8-b712-4b8b-a99d-b7788ea2a6bd%22%7d) <br>- Continue development",
 
    
    "- Teams set up their own meetings to review progress <br>- Plan for Day 2"
  ),
  stringsAsFactors = FALSE
)

md_to_anchor <- function(text) {
  gsub("\\[(.*?)\\]\\((.*?)\\)", "<a href='\\2'>\\1</a>", text, perl = TRUE)
}

schedule_1 |> 
  #dplyr::mutate(across(c(Activity, Details), ~ md_to_anchor(.))) |>
  kable("markdown", escape = FALSE) #|> 
  #kable_styling()

#kable(schedule_1, format = "markdown")

```

### 📅 Day 2: 4th September 2025

**Rooms booked**

```{r, echo=FALSE, warning=FALSE}

rooms_2 <- data.frame(
  Location = c("Coventry", "Darlington", "London", "Sheffield"),
  Room = c("CH S2.4 (10) VC", "BGH L0-3 (14) VC", "SB LG.03/LG.04 (30) VC", "SPP 4-10 (10) VC")
)
knitr::kable(rooms_2, format = "markdown")

```

**Agenda**
```{r, echo=FALSE, warning=FALSE}
library(knitr)

schedule2 <- data.frame(
  Time = c(
    "10:00 – 10:30", 
    "10:30 – 11:00",
    "11:00 – 12:00",
    "12:00 – 13:00",
    "13:00 – 15:00", 
    "15:00 – 15:45",
    "15:45 – 16:45", 
    "16:45 – 17:00"
  ),
  Activity = c(
    "🟢 [Morning Kickoff on MS Teams](https://teams.microsoft.com/l/meetup-join/19%3ameeting_OTc5YTg2ODUtNWRkOC00ODAyLWJkMDMtYzJiMDMzOWI2NGMy%40thread.v2/0?context=%7b%22Tid%22%3a%22fad277c9-c60a-4da1-b5f3-b3b8b34a82f9%22%2c%22Oid%22%3a%2273293cd8-b712-4b8b-a99d-b7788ea2a6bd%22%7d)",
    "💬 Team Check-In",
    "💻 Hacking Session #4",
    "🍽️ Lunch Break",
    "💻 Hacking Session #5",    
    "🖼️ Presentation Prep", 
    "🎤 [Project Demos & Voting on MS Teams](https://teams.microsoft.com/l/meetup-join/19%3ameeting_ZTFlNmQ2NjItMDFmOC00OTM2LTlkNmMtMGQ2NTNiMWE3MWNl%40thread.v2/0?context=%7b%22Tid%22%3a%22fad277c9-c60a-4da1-b5f3-b3b8b34a82f9%22%2c%22Oid%22%3a%2273293cd8-b712-4b8b-a99d-b7788ea2a6bd%22%7d)", 
    "🏆 [Awards & Closing Remarks on MS Teams](https://teams.microsoft.com/l/meetup-join/19%3ameeting_ZTFlNmQ2NjItMDFmOC00OTM2LTlkNmMtMGQ2NTNiMWE3MWNl%40thread.v2/0?context=%7b%22Tid%22%3a%22fad277c9-c60a-4da1-b5f3-b3b8b34a82f9%22%2c%22Oid%22%3a%2273293cd8-b712-4b8b-a99d-b7788ea2a6bd%22%7d)"
  ),
  Details = c(
    
    # Morning Kickoff"
    "- Recap of Day 1 <br>- Final reminders & presentation tips",
    #team check in 
    "- Teams set up their own meetings for morning sync and planning",
    #hacking session 4
    "- [MS Teams Drop-in: Git (10:30 - 11:00)](https://teams.microsoft.com/l/meetup-join/19%3ameeting_ZTlkZWE0ODAtOTg2Yy00ODUxLWJmOGUtMDRkYmMyMTQzNDE0%40thread.v2/0?context=%7b%22Tid%22%3a%22fad277c9-c60a-4da1-b5f3-b3b8b34a82f9%22%2c%22Oid%22%3a%2273293cd8-b712-4b8b-a99d-b7788ea2a6bd%22%7d) <br>- [MS Teams Drop-in: RShiny (11:00 - 11:30)](https://teams.microsoft.com/l/meetup-join/19%3ameeting_YTgzYjJlMWMtZTQzYy00ZjNkLWIyNjUtNzZjMDU5OGQwMDkx%40thread.v2/0?context=%7b%22Tid%22%3a%22fad277c9-c60a-4da1-b5f3-b3b8b34a82f9%22%2c%22Oid%22%3a%2273293cd8-b712-4b8b-a99d-b7788ea2a6bd%22%7d) <br>- Continue development",

    
    #lunch
     "- Lunch is not provided but feel free to bring your own",
    
#hacking session 5
        "- [Drop in: Focus on LLMs & (13:00 - 13:30)](https://teams.microsoft.com/l/meetup-join/19%3ameeting_M2M0NjgwODQtMjAxNS00ZjY4LWJmYmEtMTkyZGNiYmZhZTM1%40thread.v2/0?context=%7b%22Tid%22%3a%22fad277c9-c60a-4da1-b5f3-b3b8b34a82f9%22%2c%22Oid%22%3a%2273293cd8-b712-4b8b-a99d-b7788ea2a6bd%22%7d) <br>- [Drop in: Automated QA (13:30 - 14:00)](https://teams.microsoft.com/l/meetup-join/19%3ameeting_NGU0YTFiMTQtOTYyOC00OTY1LWJlZTAtOGEwMTRkMTIxNTE1%40thread.v2/0?context=%7b%22Tid%22%3a%22fad277c9-c60a-4da1-b5f3-b3b8b34a82f9%22%2c%22Oid%22%3a%2273293cd8-b712-4b8b-a99d-b7788ea2a6bd%22%7d) <br>- [Drop in: EES API (14:00 - 14:30)](https://teams.microsoft.com/l/meetup-join/19%3ameeting_ODRkYTQ0MDUtYjk4NS00NWY4LTgwNmMtNGU2Y2FhM2NiZGI1%40thread.v2/0?context=%7b%22Tid%22%3a%22fad277c9-c60a-4da1-b5f3-b3b8b34a82f9%22%2c%22Oid%22%3a%2273293cd8-b712-4b8b-a99d-b7788ea2a6bd%22%7d) <br>- Continue development",
  
   
    #presentation

    "- Finalise project <br>- Create and polish final presentations",
    
    #project demos
    "- Team presentations <br>- Audience voting",
    #closing
    "- Announce award winners <br>- Final thoughts"
  ),
  stringsAsFactors = FALSE
)

kable(schedule2, format = "markdown")
```
:::
