---
title: " `r params$proj_name` - Hackathon Project Brief"
format: 
  html:
    embed-resources: true
    toc: true
engine: knitr
params:
  proj_name: "Project name"
  proj_desc: "Project description"
  proj_important: "This project is important because"
  proj_solution: "This project will solve the problem by"
  proj_data_1: "Data needed for the project..."
  proj_data_2: "Data availability..."
  proj_code: "Existing code available..."
  proj_tools: "Tools to use for the project..."
  proj_know: "A subject knowledge expert will/will not be available"
  proj_real: "Realistic expectations for the project..."
  proj_chall: "Known challenges and limitations..."
  proj_info: "Other information about the project..."
  proj_datacamp: "Data camp courses you can use ..."
  proj_other_resources: "Other resources you can use ..."
  proj_skills: "Skills you will develop by working on this project"
editor: visual
---

## 💡 Project Information {#project-info}

::: callout-tip
These details are provided by the teams who proposed the project. You can use this section to help you plan your project and your presentation.
:::

### The problem the project aims to solve

`r params$proj_desc`

### Why is this project important/interesting to explore

`r params$proj_important`

### Skills you will develop by working on this project

`r params$proj_skills`

### Known challenges and limitations to the project

```{r, results='asis', echo=FALSE}

if (params$proj_chall == "") {
  cat("No known challenges or limitations were provided for this project.\n")
} else {
  cat(params$proj_chall, "\n")
}

```


### Vision for the project by end of hackathon

::: callout-tip
This is the vision that the team who proposed the project had in mind for the end result of the hackathon. However, if you have a different idea for the end result that would work better, we encourage you to go with your idea
:::

```{r, results='asis', echo=FALSE}

if (params$proj_real == "") {
  cat("The team who proposed this project did not have a specific vision for the end product of this project.\n")
} else {
  cat(params$proj_real, "\n")
}

```

## 🛠 Data and tools

### Data you need

::: callout-tip
This is the data you will need to use for the project. This information was provided by the team who proposed the project.
:::

#### Data information 

`r params$proj_data_1`

#### Data access

`r params$proj_data_2`

### Is there existing code you can use?

```{r, results='asis', echo=FALSE}

if (params$proj_code=="") {
  cat("No existing code is available for this project.\n")} else {
  cat(params$proj_code, "\n")
}

```

### Tools you can use

::: callout-tip
The following are tools suggested by the team that proposed the project to help you get started. Feel free to use tools that suit you and your team.
:::

```{r, results='asis', echo=FALSE}

if (params$proj_tools == "") {
  cat("No specific tools are required for this project.\n")
} else {
  cat(params$proj_tools, "\n")
}

```


## 🤝 Support available

### Support for data background about the project

```{r, results='asis', echo=FALSE}

if (params$proj_know == "") {
  cat("No subject matter expert is available for this project.\n")
} else {
  cat(params$proj_know, "\n")
}

```

### Online courses and resources to help upskill

#### DataCamp

::: callout-tip
Don't have a DataCamp license? Email Lisa Smyth at [datacamp.requests\@education.gov.uk](mailto:datacamp.requests@education.gov.uk) ccing your line manager to get your license before the hackathon!
:::

```{r, results='asis', echo=FALSE}

if (params$proj_datacamp == "") {
  cat("No DataCamp courses were provided for this project.\n")
} else {

sen <- stringr::str_split_1(params$proj_datacamp, ";")

  for (i in sen){
    
    cat("- ", i,"\n")
  }}
```

#### Other resources

```{r other_resources , results='asis', echo=FALSE}

if (isTRUE(nzchar(params$proj_other_resources))) {
  sen <- stringr::str_split_1(params$proj_other_resources, ";")
  for (i in sen) {
    cat("- ", i, "\n")
  }
} else {
  cat("No other resources were provided for this project.\n")
}



```

